LV2

### 2018-04-19 paper.tex
Tweet collection procedure

\usepackage{todonotes}

\usepackage{mathptmx}

@@

%There are several challenges of building a tweet collection that adequately represents language use in the country.
%
Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}. However, such an approach is not suitable for Russian tweets, because tweets that originate from Russia and other countries would inevitably be collected, and English, because of the same issue, but on a much larger scale.
%
For the same reason, a TREC-like collection building approach \cite{lin2016overview} of filtering the publicly available stream of tweets by language would not work.
%
A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective but might lead to a biased collection if the list is not diverse. Also, tracking personal accounts is problematic because of privacy concerns.
%
A geo-location based collection procedure produces representative results \cite{milajevs:2017:BUCC}. It is not biased linguistically because it is based neither on a list of keywords nor on a list of users. Unfortunately, a large number of tweets is not geo-located, which makes retrieval incomplete.

>>>>

\usepackage{soul}
\definecolor{hlcolor}{RGB}{255, 221, 163}
\sethlcolor{hlcolor}
\usepackage{mathptmx}

@@

%%%%%%%%%
% Problem
%%%%%%%%%
%There are several challenges of building a tweet collection that adequately represents language use in the country.
%
Building a monolingual Latvian collection could be done by harvesting tweets that contain indicative Latvian words which do not present in other languages, similarly how it is done for Dutch \cite{sang2013}. However, such an approach is not suitable for tweets in Russian and English, as these languages are widely used outside of Latvia.
%
For the same reason, a TREC-like collection building approach \cite{lin2016overview} of filtering the publicly available stream of tweets by language would not work.
%
A tweet collection based on a curated list of users \cite{SANVICENTE16.465} is effective but might lead to a biased collection if the list is not diverse. Also, tracking personal accounts is problematic because of privacy concerns.
%
A geo-location based collection procedure produces representative results \cite{milajevs:2017:BUCC}. It is not biased linguistically because it is based neither on a list of keywords nor on a list of users. Unfortunately, a large number of tweets is not geo-located, which makes retrieval incomplete.

%%%%%%%%
% Method
%%%%%%%%
To keep a balance between privacy and objectivity maximizing completeness, this work applies a hybrid approach by combining a geo-location based collection procedure with tracking a curated list of users. To minimize privacy issues, only accounts of organizations and public figures are tracked.

%%%%%%%%%
% Results
%%%%%%%%%

%%%%%%%%%%%%%
% So, what...
%%%%%%%%%%%%%

\section{Data collection}
\label{sec:data-collection}

Over the period from 15 April 2017 to \hl{19 April 2018} the initial set of \hl{1\,685\,048} tweets were collected from the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnotemark{}
%
\footnotetext{\url{https://developer.twitter.com/en/docs/tweets/filter-realtime/api-reference/post-statuses-filter}}
%
The \texttt{locations} parameter was set to the bounding box of Riga, the capital of Latvia.\footnotemark{}
%
\footnotetext{The coordinates of the bounding box are \texttt{23.9325829, 56.8570671, 24.3247299, 57.0859184}.}
%
In addition to the location, \hl{420} accounts were tracked. \hl{The whole list of screen names together with user ID is available in the supplement.}

To comply with Twitter's terms of service, on \hl{19 April 2018}, the raw tweet data was redownloaded (or rehydrated) to get rid of deleted tweets. In addition to that, the tweets that originated a retweet were added to the collection. Also, we have noticed a large number of tweets that come from Sweden (probably because of the imprecise \texttt{locations} parameter value), so the tweets which location country code was \texttt{SE} were omitted. This resulted in \hl{1\,133\,812} tweets that formed the final collection presented here.
